SubsidyExplorer - Step 1: Data Wrangling

### 2020-10-15 scripts/01_data_wrangling.Rmd
formatting and country profile minor edits

# Load data
fao_production_dat <- read.csv(paste0(fao_production_path, "TS_FI_CAPTURE.csv")) %>%
  clean_names(case = "snake") %>%
  dplyr::filter(year >= 2000) %>%
  dplyr::filter(unit == "t") %>% # remove catches measured in number of individuals
  mutate(species = as.character(species)) %>%
  left_join(fao_country_lookup, by = "country") %>%
  inner_join(fao_area_lookup, by = c("fishing_area" = "area")) %>%
  group_by(iso3, year, species, fishing_area) %>%
  summarize(value = sum(quantity, na.rm = T)) %>%
  ungroup() %>%
  left_join(fao_species_lookup, by = "species")

>>>>

# Load data
fao_production_dat <- read.csv(paste0(fao_production_path, "TS_FI_CAPTURE.csv")) %>%
  clean_names(case = "snake") %>%
  dplyr::filter(year >= 2000) %>%
  dplyr::filter(unit == "t") %>% # remove catches measured in number of individuals
  mutate(species = as.character(species)) %>%
  left_join(fao_country_lookup, by = "country") %>%
  inner_join(fao_area_lookup, by = c("fishing_area" = "area")) %>%
  dplyr::filter(fishing_area > 10) %>% # remove inland fishing
  group_by(iso3, year, species, fishing_area) %>%
  summarize(value = sum(quantity, na.rm = T)) %>%
  ungroup() %>%
  left_join(fao_species_lookup, by = "species")
